Deciding to Disclose

### 2015-06-22 model_description.tex
Expanding the model build process

In this section we sketch the process of moving from a real world scenario, to a minimal game which sufficiently captures reality. For a

@@

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

>>>>

@@

In order to translate the scenario sketched above into a more abstract, tractable form, we can treat it as a game. A game, in the game theoretic sense, this can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}). Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/simplest_game}
\end{adjustbox}
\caption{A very simple two player game.}

\label{fig:simplest_game}
\end{figure}

The first complication, is that there should be differentiation between referring, and doing nothing because specialist treatment incurs a cost. We can modify the payoffs to reflect this, by reducing the midwife's payoffs when they refer. If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help is to do nothing.

This simple game is, however not very informative and clearly neglects much of the nuance of the scenario. The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves. In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what they have claimed about it.
To reflect this, we would need different variations on the same game to reflect this attribute.

To resolve this, we can do exactly that, and cast it as a signalling game. We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one (fig \ref{fig:less_simple}).

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/less_simple_game}
\end{adjustbox}
\caption{A less simple two player game.}

\label{fig:less_simple}
\end{figure}

Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
